---
title: "Weight of Fish"
author: "ediaz16"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

## read in fishy data
```{r}
fishAll = read_csv('Fish.csv')
```


# Predicting Fish Weight


## Perch

```{r}
perchFish = filter(fishAll, Species=='Perch')
perchModel = lm (Weight~Length1+Length2+Length3+Height+Width,data=perchFish)
summary.lm(perchModel)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ Length1 + Length2 + Length3 + Height + Width,
               data = perchFish,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
  
## Which is best??  

Model #2

```{r}
which.max(summary.out$adjr2)
```
### Best Models
We find best models for all three species

### Best Two regressor model
```{r}
#best model
perchBest2=lm(Weight~Height+Width, data=perchFish)
summary.lm(perchBest2)
```





## Pike

```{r}
pikeFish = filter(fishAll, Species=='Pike')
pikeModel = lm (Weight~Length1+Length2+Length3+Height+Width,data=pikeFish)
summary.lm(pikeModel)
```
```{r}


regsubsets.out <-
    regsubsets(Weight ~ Length1 + Length2 + Length3 + Height + Width,
               data = pikeFish,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

Best two variables for pike are Length1 and Length3

### Best Models

### Best Two regressor model
```{r}
#best model
pikeBest2=lm(Weight~Height+Width, data=pikeFish)
summary.lm(pikeBest2)
```

## Roach
```{r}
RoachFish = filter(fishAll, Species=='Roach')
RoachModel = lm (Weight~Length1+Length2+Length3+Height+Width,data=RoachFish)
summary.lm(RoachModel)
```

### Best Models
```{r}

regsubsets.out <-
    regsubsets(Weight ~ Length1 + Length2 + Length3 + Height + Width,
               data = RoachFish,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

### Best Two regressor model

The best  two variables to predict weight are Length3 and Width

```{r}
#best model
RoachBest2=lm(Weight~Length3+Width, data=RoachFish)
summary.lm(RoachBest2)
```

## Final Summary Statements